Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-16 src/tex/ms.tex
text on individual events

\section{Results}
\label{sec:Results}
In this section, we present the results of our study.
We first show the PE results of all events and present the results of Bayesian hierarchical modeling.
Then, we will discuss some special events individually.

@@

\subsection{Result on GWTC-3}
% Violin plot
In figure \ref{fig:violin_kappa}, we show the posterior of $\kappa$ for each event in the form of a violin plot.
The median and confidence interval of $\kappa$ are calculated with the restricted posterior distribution of $\kappa$, which is given by equation \ref{eq:restricted_posterior}.
We excluded GW200129 from the calculation of collective analysis.
Details of the exclusion are discussed in Sec.~\ref{sec:GW200129}.

>>>>

\section{Results}
\label{sec:Results}

In this section, we present the results of our study.
We first show the PE results of all events and present the results of Bayesian hierarchical modeling.
Then, we will discuss some special events individually.

@@

\subsection{Result on GWTC-3}

% Violin plot
We present the result of our catalog analysis in Fig.~\ref{fig:violin_kappa}.
This shows the posterior distribution on $\kappa$ (abscissa) obtained for each event (ordinate), colored by the distance of the respective posterior mean from the origin in units of standard deviation, i.e., $|\mu/\sigma|$.
The collective measurement obtained by assuming a shared $\kappa$ across events, Eq.~\eqref{eq:restricted_posterior}, is represented by its 90\%-credible symmetric interval (blue band) around the median (blue line);
this joint measurement is fully consistent with $\kappa = 0$ (dashed line), meaning we find no evidence for birefringence.

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are \mi{THOMAS: list 3-5 events with the narrowest posterior---maybe also add a little table showing their median $\pm$ their 90\% CL, like $\tilde{\kappa}^{+x}_{-y}$ where $\tilde{\kappa}$ is the posterior median value, $x$ is the distance from the median to the 95\% percentile and $y$ is the distance to the 5\% percentile}

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| = \dots$ \mi{THOMAS: fill in these values}

We excluded GW200129 from the calculation of collective analysis.
Details of the exclusion are discussed in Sec.~\ref{sec:GW200129}.
